%! TEX TS-program = lualatex
\documentclass[a4paper]{article}

\usepackage{textcomp}
\usepackage[english]{babel}

\newcommand\ESCAPE{\textbf{ESCAPE TAG}}
\newcommand\ZWJ{\textbf{ZERO WIDTH JOINER}}
\usepackage{fontspec}

\author {Mm2PL}
\title {Emoji RFC}

\begin{document}
    \maketitle
    \begin{center}
        \small{Version: 1.1}
    \end{center}

    \begin{section}{Abstract}
        The Unicode character \ZWJ{} (U+200D) has been banned from Twitch Chat.
        This document describes an alternate emoji joining scheme.

        The key words "MUST", "MUST NOT", "REQUIRED", "SHALL", "SHALL NOT",
        "SHOULD", "SHOULD NOT", "RECOMMENDED",  "MAY", and "OPTIONAL" in this
        document are to be interpreted as described in RFC 2119.
    \end{section}
    \begin{section}{Emoji joining in Unicode}
        Unicode uses the \ZWJ{} character to combine
        multiple emoji into a single pictogram. Many of these combined emoji
        are not available on Twitch Chat. For example \textbf{man farmer} consists of:
        \begin{itemize}
            \item \textbf{MAN}
            \item \textbf{ZERO WIDTH JOINER}
            \item \textbf{EAR OF RICE}
        \end{itemize}
        
        While on Twitch it renders as:
        \begin{itemize}
            \item \textbf{MAN}
            \item \textbf{EAR OF RICE}
        \end{itemize}
    \end{section}
    \begin{section}{The solution to this problem}
        The solution is quite simple. Encoding the \ZWJ{} as another character or
        sequence of characters, preferably invisible ones. The character that
        was decided on is \textbf{U+E0002}. It has has no official name, in
        this document it will be called \ESCAPE{}. Its properties are quite
        unique:
        \begin{enumerate}
            \item It has no glyph.
            \item It is not a space.
            \item It is not filtered by Twitch.
        \end{enumerate}
        Before processing a message the \ESCAPE{} character MUST be replaced
        with \ZWJ{} unless its proceeded with another \ESCAPE{}, in which case
        it MUST NOT replaced. The suggested regular expression that SHOULD be
        used for replacing \ESCAPE{} with \ZWJ{} is:
        \begin{verbatim}
            (?<!\U000E0002)\U000E0002
        \end{verbatim}
        Where:
        \begin{enumerate}
            \item \verb`\U000E0002` is \ESCAPE{}
        \end{enumerate}
    \end{section}
\end{document}
